\documentclass{tccv}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\begin{document}

\part{João P.C. Lopes}

\section{Public projects}

\begin{yearlist}

\item{2014}
    {Masters Thesis \newline
    (\href{http://jlopes.pt/thesis}{jlopes.pt/thesis})}
    {Framework integration solution focused on bridging the gap between the development and the simulation of multi-agent systems.}

\item{2014}
    {Stock Portfolio \newline
    (\href{https://github.com/lopis/StockPortfolioUbuntu}{github/lopis/StockPortfolioUbuntu})}
    {Simple stock ticker app for Ubuntu phone; my first experience with the Ubuntu SDK and Ubuntu Phone environment.}

\item{2014}
    {Jadex Tutorial \newline
    (\href{http://paginas.fe.up.pt/~ei10009/jadex/doku.php}{fe.up.pt/~ei10009/jadex/doku.php})}
    {Jadex reference page created for students, created as a Student Assistant for an AI course}

\item{2013}
    {TchiRSS \newline
    (\href{https://github.com/lopis/tchiRSS}{github/lopis/tchiRSS})}
    {A web app created as a hobby to easily track changes to RSS feeds without having to rely on other services. Still ocasionally updated. }

\item{2013}
    {Frown API \newline
    (\href{https://github.com/lopis/frown}{github/lopis/frown})}
    {A REST web service that powers avatar enabled applications using SVG.
    Built in PHP using CodeIgniter.}

\item{2012}
    {Guess Me Out \newline
    (\href{https://github.com/lopis/Guess-Me-Out}{github/lopis/Guess-Me-Out})}
    {An on-line, social ``guess who'' mobile game for meeting new people.
    Developed for \emph{Android} devices; webservice in \emph{Rails}.}

\item{2012}
    {City Bomber \newline
    (\href{https://github.com/lopis/citybomber}{github/lopis/citybomber})}
    {A location-based game of ``bomberman'' where players are supposed
    to take down each other with bombs placed in the field with augmented reality. \emph{Android} game with \emph{Java} backend.}

\end{yearlist}

\section{Skills}
\begin{factlist}
\item{Programming}
    {Java, JS, Node, HTML, CSS, PHP, CodeIgniter, Ruby, Rails, \LaTeX, SQL, Python
}
\item{Tools}
    {Eclipse, Linux, Git, Android SDK, Ubuntu SDK, JDT}

\item{Misc}
    {Photoshop, Vectorial, Drawing, 3D Modelling, }

\end{factlist}

\personal[www.jlopes.pt]
    {www.github.com/lopis}
    {Porto, Portugal}
    {joaopclopes@gmail.com}

\section{Teaching experience}

\begin{eventlist}

\item{Jul 2014}
    {Faculty of Engineering, U Porto}
    {Monitor for Junior Students}

For two weeks, I lectured and assisted high school students in developing 3D animations using the visual programming environment Alice.

\item{Sep 2013 -- Jan 2014}
    {Faculty of Engineering, U Porto}
    {Monitor for AI course}

I assisted students in the development of their semester-long ``Agents and Distributed AI'' projects and also produced an extensive tutorial about Jadex.

\end{eventlist}



\section{Education}

\begin{yearlist}

\item[MIEIC/FEUP]{2010 -- 2014}
    {Integrated Masters in IT Engineering and Computation}
    {(Grade: 15)
    \newline University of Porto}

\item[LEI/UMa]{2008 -- 2010}
    {IT Engineering}
    {University of Madeira}
\end{yearlist}

\section{Interests}
\begin{factlist}
    \item{}{Software Development}
    \item{}{Artificial Intelligence}
    \item{}{Interaction}
    \item{}{Web Development}
    \item{}{Mobile Applications}
    \item{}{Cooking and cycling}
\end{factlist}

\section{Writing and Speech}
\begin{factlist}
\item{Portuguese}{Native speaker}
\item{English}{Oral: fair -- Written: good}
\item{Spanish}{Oral: fair -- Written: fair}
\item{German}{Oral: some -- Written: some}
\end{factlist}



\end{document}
