%!TEX root = ../cv.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% \iffalse %%%%
%                                                                              %
%  Copyright (c) 2014 - Michiel Helvensteijn   (www.mhelvens.net)              %
%                                                                              %
%  Please don't modify and distribute the LaTeX code of my personal CV.        %
%  The cv.tex file and the rubric files are not released under an open         %
%  source license. That's only the my-cv.cls and my-whenprinting.sty files.    %
%                                                                              %
%  I include these files merely as a usage example.                            %
%                                                                              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% \fi %%%%

\begin{rubric}{Portfolio}
	\in{2013}
		Stock Portfolio is a simple stock ticker app for Ubuntu phone and was
		my first experience with the Ubuntu	SDK and Ubuntu Phone environment.
		\pdfurl{https://github.com/lopis/StockPortfolioUbuntu}
	\in{}
		As a Student Assistant for an AI course, I developed a Jadex reference page
		for students to consult while developing their AI projects.
		\pdfurl{http://paginas.fe.up.pt/~ei10009/jadex/doku.php}
	\in{}
		TchiRSS is a web app I created as a hobby to easily track changes to my
		RSS feeds without having to rely on other services. I still make
		ocasional updates to it. 
		\pdfurl{https://github.com/lopis/tchiRSS}
	\in{}
		Frown API is a REST web service that powers avatar enabled applications using SVG.
		\pdfurl{https://github.com/lopis/frown}
	\in{2011}
		Guess Me Out is an on-line, social ``guess who'' mobile game for meeting new people.
		Game developed for \emph{Android} devices and webservice in \emph{Rails}. This
		project is no longer active. \pdfurl{https://github.com/lopis/Guess-Me-Out}
	\in{}
		City Bomber is a location-based game of ``bomberman'' where players are supposed
		to kill each other with bombs placed in the field with augmented reality.
		\pdfurl{https://github.com/lopis/citybomber}
\end{rubric}
